comgen-outline

### 2017-07-10 paper/appendix-cueValidity.Rmd
fix knitting issues

```{r, cache = F}
cv.bothquestions.bars <- d.cv.bothtasks %>%
  mutate(type = factor(type, levels = c( "false", "undiagnostic","diagnostic"))) %>%
  ggplot(., aes ( x = item, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge(0.5),
           width = 0.5, color = 'black', fill = 'white')+
  geom_errorbar(position = position_dodge(0.5), width = 0.3)+
  facet_grid(task~type, scales = 'free')+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  geom_hline(data = theoretical.cv, aes(yintercept = cv), lty = 2)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        strip.text.y = element_text(angle = 0))+
  xlab("")+
  ylab("Cue validity")+
  guides(color = F)
```

```{r dq.histogram, fig.width = 3}
dq.histograms <- ggplot(d.cv.targets %>%
         filter(item %in% undiagnostic.props$item), aes( x = response ))+
  geom_histogram() + 
  facet_wrap(~item, nrow = 1) + 
  scale_x_continuous(breaks = c(0, 1))+
  scale_y_continuous(breaks = c(0, 10))
```

>>>>

```{r}
cv.bothquestions.bars <- d.cv.bothtasks %>%
  mutate(type = factor(type, levels = c( "false", "undiagnostic","diagnostic"))) %>%
  ggplot(., aes ( x = item, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge(0.5),
           width = 0.5, color = 'black', fill = 'white')+
  geom_errorbar(position = position_dodge(0.5), width = 0.3)+
  facet_grid(task~type, scales = 'free')+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  geom_hline(data = theoretical.cv, aes(yintercept = cv), lty = 2)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        strip.text.y = element_text(angle = 0))+
  xlab("")+
  ylab("Cue validity")+
  guides(color = F)
```

```{r dq.histogram, fig.width = 3}
dq.histograms <- ggplot(d.cv.targets %>%
         filter(item %in% undiagnostic.props$item), aes( x = response ))+
  geom_histogram() + 
  facet_wrap(~item, nrow = 1) + 
  scale_x_continuous(breaks = c(0, 1))+
  scale_y_continuous(breaks = c(0, 10))+
  xlab("Direct question response")+
  ylab("Number of responses")
```

### 2017-07-10 paper/comgen-paper.Rmd
fix knitting issues

```{r habituals-predictive-bda-figure, eval = F}
fig.hab.freq.predictive.vs.past <- left_join(
  rs.habituals.bda.predictive.summary %>% filter(key == "logannualRate"),
  unique(d.hab.predictive %>% 
    select(item, condition, logAnnualPastRate)
  )) %>% ggplot(., 
       aes(x=logAnnualPastRate, y = MAP, 
                              ymin = cred_lower, ymax = cred_upper, 
                              fill = condition, shape=condition))+
  geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
  scale_shape_manual(values=c(21,22,23))+
  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
  # #geom_errorbar(width=0.1)+
  scale_x_continuous(limits = c(-4,7), 
                     breaks = c(-4, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(-4,7), 
                     breaks = c(-4, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
  guides(fill=F, shape=F)+
  scale_fill_solarized()+
  xlab("Past frequency (log scale)")+
  ylab("Predicted frequency MAP (log scale)")+
  theme(axis.text.x = element_text(angle = 90))
```

@@

d.hab.predictive.endorsment.summary <- left_join(
  d.hab.predictive.endorsment.summary,
  rs.habituals.bda.predictive.summary %>% 
    filter(key == "logannualRate") %>%
    rename(logAnnualFutureRate = MAP,
         future_lower = cred_lower, future_upper = cred_upper)
  # %>%
  #   rowwise() %>%
  #   mutate(future_lower = ifelse(future_lower < -4, -4, future_lower),
  #          future_upper = ifelse(future_upper > 7, 7, future_upper))
)

>>>>

```{r habituals-predictive-bda-figure, eval =F}
fig.hab.freq.predictive.vs.past <- left_join(
  rs.habituals.bda.predictive.summary %>% filter(key == "logannualRate"),
  unique(d.hab.predictive %>% 
    select(item, condition, logAnnualPastRate)
  )) %>% ggplot(., 
       aes(x=logAnnualPastRate, y = MAP, 
                              ymin = cred_lower, ymax = cred_upper, 
                              fill = condition, shape=condition))+
  geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
  scale_shape_manual(values=c(21,22,23))+
  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
  # #geom_errorbar(width=0.1)+
  scale_x_continuous(limits = c(-4,7), 
                     breaks = c(-4, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(-4,7), 
                     breaks = c(-4, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
  guides(fill=F, shape=F)+
  scale_fill_solarized()+
  xlab("Past frequency (log scale)")+
  ylab("Predicted frequency MAP (log scale)")+
  theme(axis.text.x = element_text(angle = 90))
```

@@

d.hab.predictive.endorsment.summary <- left_join(
  d.hab.predictive.endorsment.summary,
  d.hab.predictive.summary %>%
    rename(logAnnualFutureRate = mean,
         future_lower = ci_lower, future_upper = ci_upper)
  # rs.habituals.bda.predictive.summary %>% 
  #   filter(key == "logannualRate") %>%
  #   rename(logAnnualFutureRate = MAP,
  #        future_lower = cred_lower, future_upper = cred_upper)
  # %>%
  #   rowwise() %>%
  #   mutate(future_lower = ifelse(future_lower < -4, -4, future_lower),
  #          future_upper = ifelse(future_upper > 7, 7, future_upper))
)
